\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-10-21 main.tex
Updates from Overleaf

def make_ring(
    inner_radius=2.5,
    outer_radius=5,
    Lambda=1,
    length_units="um",
    square=False,
):
    if square:
        name = "square_ring"
        outer = geo.square(outer_radius * 2, points_per_side=60)
        inner = geo.square(inner_radius * 2, points_per_side=20)
        bbox = geo.square(outer_radius * 2 * 1.4, points_per_side=5)
    else:
        name = "circular_ring"
        outer_points = geo.circle(outer_radius)
        inner_points = geo.circle(inner_radius)
        bbox = geo.circle(outer_radius * 1.4, points=21)

    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
    films = [sc.Polygon("ring", layer="base", points=outer_points)]
    holes = [sc.Polygon("hole", layer="base", points=inner_points)]
    abstract_regions = [
        sc.Polygon("bounding_box", layer="base", points=bbox),
    ]
    return sc.Device(
        name,
        layers=layers,
        films=films,
        holes=holes,
        abstract_regions=abstract_regions,
        length_units=length_units,
    )
\end{minted}
\captionof{listing}{A function that creates a \inline{Device} representing a circular or square ring centered at the origin.}
\label{code:device}
\end{code}

@@

\begin{code}
\begin{minted}[fontsize=\small]{python}
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 8_000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = 400
# For more meshing options, see the docstring for Device.make_mesh().

for square in (False, True):
    ring = make_ring(square=square)
    ring.make_mesh(
        min_triangles=min_triangles,
        optimesh_steps=optimesh_steps,
    )
    ax = ring.plot_mesh(figsize=(6, 6), color="k", alpha=0.5)
    ax = ring.plot_polygons(ax=ax)
\end{minted}
\captionof{listing}{Generating and visualizing the computational mesh.}
\label{code:mesh_generation}
\end{code}

@@

The output of \inline{superscreen.solve()} is a \inline{list} of \inline{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation. A \inline{Solution} encapsulates all of the information about a solved model: the \inline{Device}, applied field, circulating currents, vortices, and calculated stream functions and magnetic fields for all layers in the device. A \inline{Solution} also has methods for processing the simulation results, including:
\begin{itemize}
    \item{
    \inline{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
    }
    \item{
    \inline{Solution.current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
    }
    \item{
    \inline{Solution.interp_current_density()}: Evaluates the current density (sheet current) $\vec{J}(x, y)$ in each layer at arbitrary $(x, y)$ coordinates via interpolation.
    }
    \item{
    \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
    }
    \item{
    \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See \ref{secction:fluxoid} for more details.
    }
    \item{
    \inline{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
    }
\end{itemize}
\inline{Solutions} also have several visualization methods built in (see Section~\ref{section:overview:visualization}).

>>>>

def make_ring(inner_radius=2.5, outer_radius=5, Lambda=1, square=False):
    if square:
        outer_points = geo.square(2 * outer_radius, points_per_side=150)
        inner_points = geo.square(2 * inner_radius, points_per_side=75)
        bbox = geo.square(1.25 * 2 * outer_radius, points_per_side=10)
    else:
        outer_points = geo.circle(outer_radius, points=500)
        inner_points = geo.circle(inner_radius, points=300)
        bbox = geo.circle(1.4 * outer_radius, points=50)
    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
    films = [sc.Polygon("ring", layer="base", points=outer_points)]
    holes = [sc.Polygon("hole", layer="base", points=inner_points)]
    abstract_regions = [sc.Polygon("bbox", layer="base", points=bbox)]
    return sc.Device(
        "ring",
        layers=layers,
        films=films,
        holes=holes,
        abstract_regions=abstract_regions,
        length_units="um",
    )
\end{minted}
\captionof{listing}{A function that creates a \inline{Device} representing a circular or square ring centered at the origin.}
\label{code:device}
\end{code}

@@

\begin{code}
\begin{minted}[fontsize=\small]{python}
import matplotlib.pyplot as plt

fig, axes = plt.subplots(2, 2, figsize=(8, 8), constrained_layout=True)
# Create the Devices
ring = make_ring(square=False)
square_ring = make_ring(square=True)
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 12000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = (None, 40)
# For more meshing options, see the docstring for Device.make_mesh().
for opt_steps, row in zip(optimesh_steps, axes):
    title = f"optimesh_steps = {opt_steps}"
    for device, ax in zip((ring, square_ring), row):
        # Generate the mesh
        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
        # Visualize the mesh
        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
        device.plot_polygons(ax=ax, linewidth=3, legend=False)
        ax.axis("off")
        ax.set_title(title, fontfamily="monospace")
axes[0, 0].legend(loc="best")
\end{minted}
\captionof{listing}{Generating and visualizing the computational mesh.}
\label{code:mesh_generation}
\end{code}

@@

The output of \inline{superscreen.solve()} is a \inline{list} of \inline{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation. A \inline{Solution} encapsulates all of the information about a solved model: the \inline{Device}, applied field, circulating currents, vortices, and calculated stream functions and magnetic fields for all layers in the device. A \inline{Solution} also has methods for processing the simulation results, including:
\begin{itemize}
    \item{
    \inline{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
    }
    \item{
    \inline{Solution.grid_current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
    }
    \item{
    \inline{Solution.interp_current_density()}: Evaluates the current density (sheet current) $\vec{J}(x, y)$ in each layer at arbitrary $(x, y)$ coordinates via interpolation.
    }
    \item{
    \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
    }
    \item{
    \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See \ref{secction:fluxoid} for more details.
    }
    \item{
    \inline{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
    }
\end{itemize}
\inline{Solutions} also have several visualization methods built in (see Section~\ref{section:overview:visualization}).
